Updates on the Exoplanet Orbit Database

### 2013-12-27 draft/ms.tex
Add reference.tex. Fill in fields overlapped with Wright 2011 in table.

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}

@@

Table: complete list of table parameters. Highlight the ones not
included in Wright\etal2011

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
%\input{references.tex}

@@

OTHERNAME\dotfill & String & Other commonly used name of planet &  \\

@@

HD\dotfill & String & &  \\
HR\dotfill & String & &  \\
HIPP\dotfill & String & & \\
SAO\dotfill & & & \\
GL\dotfill & & & \\
BINARY\dotfill & & & BINARYREF BINARYURL \\
RA, RA\_STRING\dotfill & & & \\
DEC, DEC\_STRING\dotfill & & & \\

@@

BMV\dotfill & & & \\
V\dotfill & & & VREF,VURL \\
J\dotfill & & & \\
H\dotfill & & & \\
KS\dotfill & & & \\

@@

PAR\dotfill & & & PARUPPER,PARLOWER,UPAR \\
VSINI\dotfill & & & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\

@@

PER\dotfill & & & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
ECC\dotfill & & & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
OM\dotfill & & & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
K\dotfill & & & KUPPER,KLOWER,UK,KREF,KURL \\
T0\dotfill & & & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
DVDT\dotfill & & & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
I\dotfill & & & IUPPER,ILOWER,UI,IREF,IURL \\
MSINI\dotfill & & & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
A\dotfill & & & AUPPER,ALOWER,UA,AREF,AURL \\

@@

TREND\dotfill  & & & \\
LAMBDA\dotfill & & & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\

@@

FREEZE\_ECC\dotfill & & & \\

@@

DEPTH\dotfill & & & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
T14\dotfill & & & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
TT\dotfill & & & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
R\dotfill & & & RUPPER,RLOWER,UR,RREF,RURL \\
AR\dotfill & & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
B\dotfill & & & BUPPER,BLOWER,UB,BREF,BURL \\
DENSITY\dotfill & & &

@@

GRAVITY\dotfill & & &

@@

TRANSIT\dotfill & & & TRANSITREF,TRANSITURL \\

@@

@@

RMS\dotfill & & & \\
CHI2\dotfill & & & \\
NOBS\dotfill & & & \\
NCOMP\dotfill & & & \\
MULT\dotfill & & & \\
PLANETDISCMETH\dotfill & & & \\
STARDISCMETH\dotfill & & & \\
DATE\dotfill & & & \\
FIRSTREF\dotfill & & & FIRSTURL \\
ORBREF\dotfill & & & ORBURL \\

@@

MSTAR\dotfill & & & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\

@@

TEFF\dotfill & & & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\

@@

LOGG\dotfill & & & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
FE\dotfill & & & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
SHK\dotfill & & & \\
RHK\dotfill & & & \\

@@

JSNAME\dotfill & & & EPEURL \\
ETDNAME\dotfill & & & ETDURL \\
SIMBADNAME\dotfill & & & SIMBADURL \\

@@

>>>>

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}

@@

Table: complete list of table parameters. Highlight the ones not
included in \cite{Wright2011}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
\input{references.tex}

@@

OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet &  \\

@@

HD\dotfill & Long Integer & Henry Draper number of sar &  \\
HR\dotfill & Integer & Bright Star Catalog number of star &  \\
HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of star & \\
SAO\dotfill & Long Integer & SAO catalog number of star & \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \\
BINARY\dotfill & Boolean & Star known ot be binary? & BINARYREF BINARYURL \\
RA, RA\_STRING\dotfill & Double, String & J2000 right ascension in decimal hours and in
sexagesimal string & \\
DEC, DEC\_STRING\dotfill & Double, String & J2000 declination in decimal degrees and in
sexagesimal string & \\

@@

BMV\dotfill & Float & $B-V$ color & \\
V\dotfill & Float & $V$ magnitude & VREF,VURL \\
J\dotfill & Float & $J$ magnitude & \\
H\dotfill & Float & $H$ magnitude & \\
KS\dotfill & Float & $K_S$ magnitude & \\

@@

PAR\dotfill & Float & Parallax in mas & PARUPPER,PARLOWER,UPAR \\
VSINI\dotfill & Float & Projected equatorial rotational velocity of
star & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\

@@

PER\dotfill & Double & Orbital period in days & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
ECC\dotfill & Float & Orbital eccentricity & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
OM\dotfill & Float & Argument of periastron in degrees & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & KUPPER,KLOWER,UK,KREF,KURL \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\
I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
systems only ZZZ still true?) & IUPPER,ILOWER,UI,IREF,IURL \\
MSINI\dotfill & Float & Minimum mass (as calculated from the mass
function) in $M_{\rm Jup}$ & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
A\dotfill & Float & Orbital semimajor axis in AU & AUPPER,ALOWER,UA,AREF,AURL \\

@@

TREND\dotfill  & Boolean & Linear trend in fit? & \\
LAMBDA\dotfill & Float & Projected spin-orbit misalignment & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\

@@

FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \\

@@

DEPTH\dotfill & Float & $(R_p/R_*)^2$ & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\
TT\dotfill & Float & Epoch of transit center in
HJD\tablenotemark{c} $-2,440,000$ & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
R\dotfill & Float & Radius of the planet in Jupiter radii & RUPPER,RLOWER,UR,RREF,RURL \\
AR\dotfill & $(a/R_*)$ & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
B\dotfill & Float & Impact parameter of transit & BUPPER,BLOWER,UB,BREF,BURL \\
DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &

@@

GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of the planet
calculated from transit parameters &

@@

TRANSIT\dotfill & Boolean & Is the planet known to transit? & TRANSITREF,TRANSITURL \\

@@

& & & \\

@@

RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \\
CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \\
NOBS\dotfill & Integer & Number of observations used in fit & \\
NCOMP\dotfill & Integer & Number of planetary companions known & \\
MULT\dotfill & Boolean & Multiple planets in system? & \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \\
STARDISCMETH\dotfill & String & Method of discovery for the first
planet in the system & \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \\
ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \\
FIRSTREF\dotfill & String & First peer-reviewed publication of
planetary orbit & FIRSTURL \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\

@@

MSTAR\dotfill & Float & Mass of host star & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\

@@

TEFF\dotfill & Float & Effective temperature of host star & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\

@@

LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
host star & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & FEUPPER,FELOWER,UFE,FEREF,FEURL \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \\

@@

JSNAME\dotfill & String & Name of host star used in the Extrasolar
Planets Encyclopaedia & EPEURL \\
ETDNAME\dotfill & String & Name of host star used in the Exoplanet
Transit Database & ETDURL \\
SIMBADNAME\dotfill & String & Valid SIMBAD name of host star & SIMBADURL \\

@@

\tablenotetext{b}{Originally as other commonly used name for star in \cite{Wright2011};
  changed to other commonly used name for planet.}
\tablenotetext{c}{ZZZ Is this now consistent? ZZZ}
